\mytable{|X[0.2,c]|X[l]}{
Acronyms & Description \\

Admin &
The operators who manage course registrations and schedule bookings based on the incoming requests from parents.
\\

API &
\textbf{Application Programming Interface}\cite{api_ref}; used in the context of REST API for communication between the frontend and backend.
\\

Commute Buffer &
An automatically calculated travel time inserted between an instructor's consecutive classes at different physical branches.
\\

DDD &
\textbf{Domain-Driven Design}\cite{ddd_ref}; a software design approach focused on modeling the system based on the core business domain.
\\

Hexagonal Architecture &
A backend architectural pattern that keeps the core scheduling domain portable and testable in isolation from the web framework and database.
\\

Modular Monolith &
A deployment architecture where the system is deployed as a single unit but internally structured into well-defined modules.
\\

Parent &
The users who provide the subject that they want their child to learn to the admin.
\\

REST &
Representational State Transfer\cite{rest_ref}; the architectural style used for designing the system's web API.
\\

SaaS &
\textbf{Software as a Service}\cite{saas_ref}; a software distribution model mentioned as out-of-scope for this project.
\\

SDLC &
Software Development Life Cycle; the framework used for planning, creating, testing, and deploying the software.
\\

XP &
Extreme Programming; an Agile software development methodology focused on software quality, combined with Kanban for this project.
\\
}